---
title: "Berlin's Neighbourhood Diversity"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    vertical_layout: fill
    theme: 
      base_font:
        google: Comfortaa
      version: 3
      bootswatch: slate
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(plotly)
library(leaflet)
library(tidyverse)
library(sf)
library(highcharter)
library(echarts4r)
library(viridis)
library(rgeos)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()


cols <- c('HK_Polen', 'HK_EheJug', 
          'HK_EheSU', 'HK_Turk', 
          'HK_Arab', 'HK_Sonst', 
          'HK_NZOrd', 'HK_EU15',
          'HK_EU28', 'no_mh')

data <- readRDS('./data/final_data.RDS')

data$lon <- st_coordinates(st_centroid(data$geometry))[, 1]
data$lat <- st_coordinates(st_centroid(data$geometry))[, 2]


data2 <- reactive({data})

a <- bslib::font_link(
  "Roboto robertson",
  href = "https://fonts.googleapis.com/css2?family=Quicksand:wght@300&display=swap"
)

```


Sidebar {.sidebar}
-------------------------------------------------------------------

```{r}
sliderInput('span', label = 'Span Parameter', min = 0.1, max = 0.9, value = 0.3, 
            step = 0.1)
```

Click and drag on the scatterplot to highlight the corresponding neighbourhoods on the map below, and click on a neighbourhood on the map to generate a chart of migration history counts & shares. The yellow line on the scatterplot represents a locally-weighted estimate of how diversity varies in Berlin by distance from the urban cores.

The dashboard is an adaption of [Kyle Walker's work](https://walkerke.shinyapps.io/neighborhood_diversity/).
</br>
</br>
<div style="text-align: left"> Data sources:
[Einwohnerregisterstatistik, Amt für Statistik Berlin-Brandenburg](https://daten.berlin.de/datensaetze/einwohnerinnen-und-einwohner-mit-migrationshintergrund-berlin-lor-planungsr%C3%A4umen-nach-8), [Senatesverwaltung für Stadtentwicklung und Wohnen, Stadtentwicklungsplan Zentren 2030](https://www.stadtentwicklung.berlin.de/planen/stadtentwicklungsplanung/download/zentren/StEP_Zentren_2030.pdf)
</div>


Row
-----------------------------------------------------------------------

### Diversity gradient

```{r}
output$scatter <- renderPlotly({
  m <- data2() %>% 
    mutate(text = glue::glue(
      "<b>{PLANUNGSRA}</b><br>Distance: {round(dist, 1)}m <br>Entropy: {round(diversity, 2)}"
    ))
  
  p1a <- ggplot(m) + 
    geom_point(alpha = 0.4, aes(dist, diversity, 
                                key = RAUMID, text = text), color = 'gray') + 
    theme_minimal(base_size = 14) + 
    stat_smooth(aes(dist, diversity), color = '#FDE725FF', method = 'loess',
                span = input$span, se = FALSE) + 
    labs(x = "", y = "") 
  
  g <- ggplotly(p1a, source = 'source', tooltip = "text") %>% 
    layout(dragmode = 'lasso', 
           yaxis = list(title = 'Diversity score', 
                        font = list(size = 5)), 
           xaxis = list(title = 'Distance from nearest urban center (m)',
                        font = list(size = 5)),
           margin = list (l = 90, b = 70),
           font = list(family = "Comfortaa", color = 'white', size = 12),
           plot_bgcolor = '#090909',
           paper_bgcolor = '#090909',
           fig_bgcolor = '#090909',
           hoverlabel = list(font = list(family = 'Comfortaa', 
                                         color = '#FDE725FF'),
                             bgcolor = '#363B40',
                             bordercolor = '#363B40')) %>% 
    event_register("plotly_selecting")
  
})

plotlyOutput('scatter', width = "80%")
```


Row
---------------------------------------------------------------------------

### Map of diversity scores

```{r}
output$map <- renderLeaflet({
  m <- data2() 
  
  pal <- colorNumeric(viridis_pal(option = 'A')(2), NULL)
  
  
  map <- leaflet(m) %>% 
    addProviderTiles('CartoDB.DarkMatter') %>% 
    clearShapes() %>% 
    addPolygons(stroke = FALSE, smoothFactor = 0,
                fillColor = ~pal(diversity), fillOpacity = 0.7,
                layerId = ~RAUMID,
                label = ~PLANUNGSRA,
                weight = .1,
                labelOptions = labelOptions(
                          style = list(
                            'color' = '#FDE725FF',
                            'font-family' = 'Comfortaa',
                            'font-weight' = 'bold',
                            'background-color' = '#363B40',
                            'background-opacity' = '0.1',
                            'border-color' = 'rgba(0,0,0,0)',
                            'box-shadow' = 'rgba(0,0,0,0)'
                          ), textsize = "11px"
                        )) %>% 
    addLegend(position = 'bottomright', pal = pal,
              values = m$diversity, title = "Score",
              opacity = 0.2
              )
  
  map
})

click_lor <- eventReactive(input$map_shape_click, {
  
  x <- input$map_shape_click
  
  y <- x$id
  
  return(y)
  
})


lor_ids <- reactive({
  eventdata <- event_data("plotly_selected", source = "source")
  if (is.null(eventdata)){
    
    return(NULL)
    
  } else {
    
    lors <- eventdata$key
    
    return(lors)
  }
  
})

observe({
  
  req(lor_ids())
  
  proxy <- leafletProxy('map')
  
  sub <- filter(data, RAUMID %in% lor_ids())
  
  box <- st_bbox(sub) %>% as.vector()
  
  
  proxy %>% 
    clearGroup(group = 'sub') %>% 
    addPolygons(data = sub, fill = FALSE, color = '#FDE725FF',
                opacity = 1, group = 'sub', weight = 1.5) %>% 
    fitBounds(lng1 = box[1],
              lat1 = box[2],
              lng2 = box[3],
              lat2 = box[4])
})


observeEvent(click_lor(), {
  
  map <- leafletProxy('map') %>% 
    removeShape('hlor') %>% 
    addPolygons(data = filter(data2(), RAUMID == click_lor()), fill = FALSE,
                              color = '#440154FF', opacity = 1, layerId = 'hlor',
                              weight = 1.6)
})


lor_data <- reactive({
  return(filter(data2(), RAUMID == click_lor()))
})

leafletOutput('map')

```


### Breakdown of migration history diversity of selected neighbourhood

```{r}
output$miplot2 <- renderEcharts4r({
  
   td <- lor_data() %>% 
     pivot_longer(
       cols = cols, 
       names_to = 'demography', 
       values_to = 'pop') %>% 
     mutate(demography = fct_recode(demography, 
                                    'EU15' = 'HK_EU15', 
                                    'EU28' = 'HK_EU28',
                                    'Poland' = 'HK_Polen',
                                    'Frm. Yugoslavia' = 'HK_EheJug',
                                    'Frm. Soviet Union' = 'HK_EheSU',
                                    'Turkey' = 'HK_Turk',
                                    'Arab' = 'HK_Arab', 
                                    'Other' = 'HK_Sonst',
                                    'Not assignable' = 'HK_NZOrd',
                                    'No migration history' = 'no_mh'))
   
   plraum <- lor_data() %>% pull(PLANUNGSRA)
   bz <- lor_data() %>% pull(BEZIRKSNAM)
   
   e_common(font_family = "Comfortaa", theme = 'dark-bold')
   
   td %>% 
     e_charts(demography) %>% 
     e_pie(pop, radius = c("50%", "70%"), 
           color = viridis(10)) %>% 
     e_legend(show = FALSE) %>% 
     e_tooltip(
       formatter = htmlwidgets::JS(
         "function(params) {
         return('<strong>' + params.name + 
         '</strong><br />Total: ' + params.value + 
         '<br />Percent: ' + params.percent) + '%'
         }"
       ),
       backgroundColor = "#363B40",
       textStyle = list(color = '#FDE725FF'),
       borderColor = "#363B40"
     ) %>% 
     e_title(paste0(plraum, ', ', bz),
             textStyle = list(fontWeight = 'normal')) %>% 
     e_color(background = '#090909')
   
     
})

echarts4rOutput('miplot2')
```


<style>

@import url('https://fonts.googleapis.com/css2?family=Comfortaa:wght@300&family=Quicksand:wght@300&display=swap');

body{ /* Normal  */
  font-size: 14px;
  font-family: Comfortaa;
  font-family: 'Light', sans-serif;
  font-weight:300;
  color:white;
}

/* Header */
h1,h2,h3,h4,5,h6{
  font-size: 24pt;
  color:white;
}


.nav-tabs-custom .nav-tabs li.active a {
  color: white;
  font-family: Comfortaa;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
  color: white;
  font-family:Comfortaa;
}

.navbar {
  background:#090909;
  background-color:#090909;
  border-color:#090909;
  color:white;
  font-family: Comfortaa;
}

.navbar-brand {
color:white!important;
}

.value-box .body {
color:white
}


.control-label {
  color:white;
  font-family: Comfortaa;
}

.sidebar.section.sidebar {
  font-family: Comfortaa;
  color: #D3D3D3;
  font-size: 8;
  text-align: justify;
}

.js-irs-0 .irs-bar {
border-top-color: #FDE725FF;
border-bottom-color: #FDE725FF;
} 

.js-irs-0 .irs-bar-edge {
border-color: #FDE725FF;
}

.js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge, .js-irs-0 .irs-bar {
background: #FDE725FF;
}

a:link {
  color: gray;
}

</style>